---
title: "DATA 211 Final Project"
author: "Brandon Conrady"
date: "4/19/2022"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
```

# Welcome to my final project.
# I am a cashier at Home Depot.
# I want to see if there is a difference in the transactions made at Self Checkouts (SCO) and regular registers (Mainline).
# I will be looking at some figures I collected to test this.

# The dataset is called "Transactions", and contains 817 entries.
# Listed are the date of the transaction, day of week, register, SCO_Flag, and total for transaction.
# SCO_Flag denotes "SCO" for SCO, and "Mainline" for all other transactions

```{r}
summary(Transactions)
```

# To get the full picture of the data we're working with, lets view the number of entries sorted by Register and SCO_Flag.

```{r}
Transactions %>%
  group_by(Register) %>%
  summarize(count = n())

Transactions %>%
  group_by(SCO_Flag) %>%
  summarize(count = n())
```

# As we can see, there are almost triple the number of SCO transactions than all other types combined.

# Next I will view the ranges of Total values sorted by Register and SCO_Flag.

```{r}
Transactions %>%
  group_by(Register) %>%
  summarize(aveTotal = mean(Total), seTotal = sd(Total)/sqrt(length(Total)), tstar = qt(1-0.05/2, length(Total) - 1)) %>%
  ggplot(aes(x = Register, y = aveTotal)) + geom_point() + geom_errorbar(aes(ymin = aveTotal - seTotal*tstar, ymax = aveTotal + seTotal*tstar))

Transactions %>%
  group_by(SCO_Flag) %>%
  summarize(aveTotal = mean(Total), seTotal = sd(Total)/sqrt(length(Total)), tstar = qt(1-0.05/2, length(Total) - 1)) %>%
  ggplot(aes(x = SCO_Flag, y = aveTotal)) + geom_point() + geom_errorbar(aes(ymin = aveTotal - seTotal*tstar, ymax = aveTotal + seTotal*tstar))
```

# As a consequence of having so many SCO entries, we can see its confidence interval is much smaller than the other types.
# Based on the graph alone, we can see that there is indeed a signifiant difference between SCO and Mainline transactions.
# However, to be safe, we will perform a t-test anyways to verify that.

# The question I will attempt to answer: "Is the amount spent at a Self Checkout significantly less than the amount spent at a regular register by customers on average?"
# Null hypothesis: mu(Mainline) = mu(SCO)
# Alternative hypothesis: mu(Mainline) > mu(SCO)


```{r}
t.test(Total~SCO_Flag, data = Transactions, alternative = "greater")
```

# Based on the low p-value, we can reject the null hypothesis.
# Furthermore, we can safely say there is evidence to back the claim that SCO transactions are significantly lower than Mainline transactions on average.
